Tree size, microhabitat, and hydraulic traits (interactively) shape drought response in a temperate broadleaf forest

### 2019-08-02 manuscript/climate_sensitivity_draft.Rmd
Update climate_sensitivity_draft.Rmd
added references to GitHub issues

    (add predictions for model without height)
    * P1.2- After accounting for height, trees currently in a dominant canopy position have lowest resistance. (partially supported)
    * P1.2alt- After accounting for height, subcanopy trees have lowest resistance. (partially supported)

@@

  * P1.3- There is a negative interactive effect between tree height and topographic water index.

@@

**3. How are functional traits distributed across size classes, and how does this affect size-resistance relationship?**

>>>>

    (add predictions for model without height- ([issue #44](https://github.com/SCBI-ForestGEO/McGregor_climate-sensitivity-variation/issues/44)))
    * P1.2- After accounting for height, trees currently in a dominant canopy position have lowest resistance. (partially supported)
    * P1.2alt- After accounting for height, subcanopy trees have lowest resistance. (partially supported)

@@

  * P1.3- There is a negative interactive effect between tree height and topographic water index. ([issue #45](https://github.com/SCBI-ForestGEO/McGregor_climate-sensitivity-variation/issues/45))

@@

**3. How are functional traits distributed across size classes, and how does this affect size-resistance relationship?**  ([issue #43](https://github.com/SCBI-ForestGEO/McGregor_climate-sensitivity-variation/issues/43))
